A general Nullstellensatz for generalized spaces

### 2019-05-08 paper-qcoh.tex
More on the subtopos case

>>>>

\begin{proof}In general, the generic model~$U_{\TT'}$ is the sheafification
of~$U_\TT$~\cite[Lemma~2.3]{caramello:definability}. By the sheaf
assumption, the objects~$U_{\TT'}$ and~$U_\TT$ actually agree as functors
on~$\Mod{\TT}_\mathrm{fp}$. Employing the lemma that computing the internal Hom
to a sheaf commutes with sheafification twice, we see that
the canonical isomorphism of Lemma~\ref{lemma:fp-double-dual} induces an
isomorphism~$a(A^\sim) \to (U_{\TT'})^{\Spec(a(A^\sim))}$ ... XXX
\end{proof}
